---
title: "Spotify's Random Playlists: Training Set"
date: today
output:
  html:
    highlight: "a11y-dark"
    css: "playlists.css"
    includes:
      in_header: "playlist-header.html"
execute:
  echo: false
  message: false
  warning: false
---


```{r}
#| label: setup
#| echo: false
#| cache: false
library(dplyr)
library(kableExtra)
```

These 25 playlists were generated from Mr. Hoffman’s library using a genuine random number generation method. Use them to develop your rules.



# Playlist \#1

```{r}
library(dplyr)
library(knitr)
library(kableExtra)

data.frame(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 4) |> 
  add_row(SONG = "God Is A Woman",        ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 4) |>
  add_row(SONG = "Objection (Tango)",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 17) |>
  add_row(SONG = "Sweet Dreams",                      ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 5) |>
  add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
  add_row(SONG = "Controlla",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 18) |>
  add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
  add_row(SONG = "Don't Bother",                     ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 9) |>
  add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
  add_row(SONG = "Grenade",                        ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
  add_row(SONG = "Drunk In Love",                     ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 9) |>
  add_row(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
  add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
  add_row(SONG = "Signs",                    ARTIST = "Drake", ALBUM = "Signs",                   YEAR = 2017, PEAK = 14) |>
  add_row(SONG = "Halo",                              ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 4) |>
  add_row(SONG = "Everything Has Changed",                  ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 7) |> 
  add_row(SONG = "Whenever Wherever",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 2) |>
  add_row(SONG = "We Found Love",            ARTIST = "Rihanna", ALBUM = "Talk That Talk",               YEAR = 2011, PEAK = 1) |>
  add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
  add_row(SONG = "I Don't Wanna Live Forever",    ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```

<br /><br />

# Playlist \#2

```{r }
data.frame(SONG = "I Don't Wanna Live Forever", ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |>
  add_row(SONG = "FourFiveSeconds", ARTIST = "Rihanna", ALBUM = "Anti", YEAR = 2016, PEAK = 3) |>
  add_row(SONG = "Thinking Out Loud", ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2014, PEAK = 1) |>
  add_row(SONG = "Jumpman", ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
  add_row(SONG = "Passionfruit", ARTIST = "Drake", ALBUM = "More Life", YEAR = 2017, PEAK = 3) |>
  add_row(SONG = "Photograph", ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
  add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover", YEAR = 2019, PEAK = 2) |>
  add_row(SONG = "Sweet Dreams", ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 5) |>
  add_row(SONG = "Problem", ARTIST = "Ariana Grande", ALBUM = "My Everything", YEAR = 2014, PEAK = 1) |>
  add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
  add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover", YEAR = 2019, PEAK = 2) |>
  add_row(SONG = "Just The Way You Are (Amazing)", ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
  add_row(SONG = "Drunk In Love", ARTIST = "Beyoncé", ALBUM = "Beyoncé", YEAR = 2013, PEAK = 9) |>
  add_row(SONG = "Grenade", ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
  add_row(SONG = "Walk On Water", ARTIST = "Beyoncé", ALBUM = "Revival", YEAR = 2017, PEAK = 7) |>
  add_row(SONG = "S&M", ARTIST = "Rihanna", ALBUM = "Loud", YEAR = 2010, PEAK = 3) |>
  add_row(SONG = "7 Rings", ARTIST = "Ariana Grande", ALBUM = "Thank U, Next", YEAR = 2019, PEAK = 1) |>
  add_row(SONG = "24K Magic", ARTIST = "Bruno Mars", ALBUM = "24K Magic", YEAR = 2016, PEAK = 5) |>
  add_row(SONG = "Billionaire", ARTIST = "Bruno Mars", ALBUM = "Lazarus", YEAR = 2010, PEAK = 3) |>
  add_row(SONG = "Halo", ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 4) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```

<br /><br />

# Playlist \#3

```{r }
data.frame(SONG = "Objection (Tango)", ARTIST = "Shakira", ALBUM = "Laundry Service", YEAR = 2001, PEAK = 17) |>
  add_row(SONG = "Break Free",            ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 16) |>
  add_row(SONG = "I Knew You Were Trouble",                 ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 2) |>
  add_row(SONG = "She Wolf",                         ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 4) |>
  add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
  add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
  add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
  add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
  add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
  add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
  add_row(SONG = "Work It Out",                       ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 7) |>
  add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
  add_row(SONG = "Don't Bother",                     ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 9) |>
  add_row(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
  add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
  add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
  add_row(SONG = "Marry You",                      ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 11) |>
  add_row(SONG = "Stay",                     ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 4) |>
  add_row(SONG = "Into You",              ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 14) |>
  add_row(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#4

```{r }
data.frame(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
add_row(SONG = "Love Story",                  ARTIST = "Taylor Swift", ALBUM = "Fearless",            YEAR = 2008, PEAK = 2) |> 
add_row(SONG = "Controlla",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 18) |>
add_row(SONG = "Shape Of You",       ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 1) |>
add_row(SONG = "The Lazy Song",                  ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "We Found Love",            ARTIST = "Rihanna", ALBUM = "Talk That Talk",               YEAR = 2011, PEAK = 1) |>
add_row(SONG = "Rude Boy",                 ARTIST = "Rihanna", ALBUM = "Rated R",                      YEAR = 2009, PEAK = 2) |>
add_row(SONG = "One Dance",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 1) |>
add_row(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
add_row(SONG = "Can't Remember To Forget",         ARTIST = "Shakira", ALBUM = "Shakira",              YEAR = 2014, PEAK = 11) |>
add_row(SONG = "Side To Side",          ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 4) |>
add_row(SONG = "You Need To Calm Down",       ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Everything Has Changed",      ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 7) |> 
add_row(SONG = "Shake It Off",                ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 2) |> 
add_row(SONG = "Objection (Tango)",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 17) |>
add_row(SONG = "Look What You Made Me Do",    ARTIST = "Taylor Swift", ALBUM = "Reputation",          YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Thinking Out Loud",  ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Crazy In Love",      ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#5

```{r }
data.frame(SONG = "I Knew You Were Trouble", ARTIST = "Taylor Swift", ALBUM = "Red",      YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Walk On Water",                     ARTIST = "Beyoncé", ALBUM = "Revival",             YEAR = 2017, PEAK = 7) |>
add_row(SONG = "Dangerous Woman",       ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 17) |>
add_row(SONG = "Crazy In Love",                     ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
add_row(SONG = "You Need To Calm Down",          ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "Billionaire",                    ARTIST = "Bruno Mars", ALBUM = "Lazarus",              YEAR = 2010, PEAK = 3) |>  
add_row(SONG = "Stay",                     ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 4) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
add_row(SONG = "Don't",              ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 8) |>
add_row(SONG = "Just The Way You Are (Amazing)", ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Best Thing I Never Had",            ARTIST = "Beyoncé", ALBUM = "4",                   YEAR = 2011, PEAK = 3) |>
add_row(SONG = "Work It Out",                       ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 7) |>
add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
add_row(SONG = "Too Good",                 ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#6

```{r }
data.frame(SONG = "God Is A Woman",        ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 4) |>
add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "Blem",                     ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 10) |>
add_row(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
add_row(SONG = "Whenever Wherever",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 2) |>
add_row(SONG = "Signs",                    ARTIST = "Drake", ALBUM = "Signs",                   YEAR = 2017, PEAK = 14) |>
add_row(SONG = "Locked Out Of Heaven",           ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "One Dance",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 1) |>
add_row(SONG = "One Last Time",         ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 2) |>
add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Stay",                     ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 4) |>
add_row(SONG = "Grenade",                        ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Problem",               ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Don't Bother",                     ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 9) |>
add_row(SONG = "Into You",              ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 14) |>
add_row(SONG = "Me!",                   ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#7

```{r }
data.frame(SONG = "Billionaire",                    ARTIST = "Bruno Mars", ALBUM = "Lazarus",              YEAR = 2010, PEAK = 3) |>  
add_row(SONG = "No Tears Left To Cry",  ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 2) |>
add_row(SONG = "Did It Again",                     ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 26) |>
add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
add_row(SONG = "Work It Out",                       ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 7) |>
add_row(SONG = "Best Thing I Never Had",            ARTIST = "Beyoncé", ALBUM = "4",                   YEAR = 2011, PEAK = 3) |>
add_row(SONG = "Too Good",                 ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
add_row(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red",      YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
add_row(SONG = "Uptown Funk",                    ARTIST = "Bruno Mars", ALBUM = "Uptown Funk",          YEAR = 2014, PEAK = 1) |>
add_row(SONG = "XO",                       ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "Blank Space",              ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 4) |> 
add_row(SONG = "Signs",                    ARTIST = "Drake", ALBUM = "Signs",                   YEAR = 2017, PEAK = 14) |>
add_row(SONG = "Hotline Bling",            ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Passionfruit",             ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 3) |>
add_row(SONG = "Walk On Water",                     ARTIST = "Beyoncé", ALBUM = "Revival",             YEAR = 2017, PEAK = 7) |>
add_row(SONG = "Look What You Made Me Do",          ARTIST = "Taylor Swift", ALBUM = "Reputation",          YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#8

```{r }
data.frame(SONG = "Work It Out",                       ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 7) |>
add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "Beautiful Liar",                   ARTIST = "Shakira", ALBUM = "B'Day",                YEAR = 2006, PEAK = 1) |>
add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Single Ladies (Put a Ring on It)",  ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 7) |>
add_row(SONG = "I Don't Wanna Live Forever",        ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
add_row(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red",           YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "Break Free",            ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 16) |>
add_row(SONG = "Look What You Made Me Do",          ARTIST = "Taylor Swift", ALBUM = "Reputation",          YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "Thinking Out Loud",  ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
add_row(SONG = "One Dance",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 1) |>
add_row(SONG = "Underneath Your Clothes",          ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 3) |>
add_row(SONG = "We Found Love",            ARTIST = "Rihanna", ALBUM = "Talk That Talk",               YEAR = 2011, PEAK = 1) |>
add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Sing",               ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
add_row(SONG = "Controlla",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 18) |>
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#9

```{r }
data.frame(SONG = "Look What You Made Me Do",                ARTIST = "Taylor Swift", ALBUM = "Reputation", YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "Side To Side",          ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 4) |>
add_row(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red",      YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Drunk In Love",                     ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 9) |>
add_row(SONG = "Objection (Tango)",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 17) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
add_row(SONG = "Grenade",                        ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Stay",                     ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 4) |>
add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Sweet Dreams",                      ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 5) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Just The Way You Are (Amazing)", ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Blem",                     ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 10) |>
add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "One Last Time",         ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 2) |>
add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
add_row(SONG = "Shake It Off", ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 2) |> 
add_row(SONG = "Fake Love",                ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2015, PEAK = 10) |>
add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#10

```{r }
data.frame(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
add_row(SONG = "Stay",                     ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 4) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
add_row(SONG = "I See Fire",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 13) |>
add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
add_row(SONG = "Love Story",               ARTIST = "Taylor Swift", ALBUM = "Fearless",            YEAR = 2008, PEAK = 2) |> 
add_row(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
add_row(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
add_row(SONG = "Umbrella",                 ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 1) |>
add_row(SONG = "Look What You Made Me Do", ARTIST = "Taylor Swift", ALBUM = "Reputation",          YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "Side To Side",          ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 4) |>
add_row(SONG = "I Knew You Were Trouble", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Too Good",                 ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Thinking Out Loud",  ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Grenade",                        ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Controlla",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 18) |>
add_row(SONG = "Locked Out Of Heaven",           ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Drunk In Love",                     ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 9) |>
add_row(SONG = "Shape Of You",       ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 1) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#11

```{r }
data.frame(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Underneath Your Clothes",          ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 3) |>
add_row(SONG = "Whenever Wherever",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 2) |>
add_row(SONG = "Can't Remember To Forget",         ARTIST = "Shakira", ALBUM = "Shakira",              YEAR = 2014, PEAK = 11) |>
add_row(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
add_row(SONG = "Dangerous Woman",       ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 17) |>
add_row(SONG = "Fake Love",                ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2015, PEAK = 10) |>
add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "One Dance",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 1) |>
add_row(SONG = "I Don't Wanna Live Forever", ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
add_row(SONG = "Break Free",            ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 16) |>
add_row(SONG = "Crazy In Love",                     ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
add_row(SONG = "Marry You",                      ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 11) |>
add_row(SONG = "Shake It Off", ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 2) |> 
add_row(SONG = "I Knew You Were Trouble", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 2) |>
add_row(SONG = "God Is A Woman",        ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 4) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#12

```{r }
data.frame(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
add_row(SONG = "Controlla",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 18) |>
add_row(SONG = "Walk On Water",                     ARTIST = "Beyoncé", ALBUM = "Revival",             YEAR = 2017, PEAK = 7) |>
add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Blank Space", ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 4) |> 
add_row(SONG = "Marry You",                      ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 11) |>
add_row(SONG = "Shake It Off", ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 2) |> 
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "Don't Bother",                     ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 9) |>
add_row(SONG = "She Wolf",                         ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 4) |>
add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Sing",               ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Can't Remember To Forget",         ARTIST = "Shakira", ALBUM = "Shakira",              YEAR = 2014, PEAK = 11) |>
add_row(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "Side To Side",          ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 4) |>
add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
add_row(SONG = "One Last Time",         ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 2) |>
add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#13

```{r }
data.frame(SONG = "Only Girl (In The World)", ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
add_row(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
add_row(SONG = "Sing",               ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "Fake Love",                ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2015, PEAK = 10) |>
add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Look What You Made Me Do", ARTIST = "Taylor Swift", ALBUM = "Reputation",          YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
add_row(SONG = "Hotline Bling",            ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "I Knew You Were Trouble", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 2) |>
add_row(SONG = "The Lazy Song",                  ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Problem",               ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 1) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "We Found Love",            ARTIST = "Rihanna", ALBUM = "Talk That Talk",               YEAR = 2011, PEAK = 1) |>
add_row(SONG = "God Is A Woman",        ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 4) |>
add_row(SONG = "Did It Again",                     ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 26) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#14

```{r }
data.frame(SONG = "Locked Out Of Heaven",           ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
add_row(SONG = "Don't",              ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 8) |>
add_row(SONG = "Fake Love",                ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2015, PEAK = 10) |>
add_row(SONG = "Shape Of You",       ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 1) |>
add_row(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
add_row(SONG = "Did It Again",                     ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 26) |>
add_row(SONG = "Billionaire",                    ARTIST = "Bruno Mars", ALBUM = "Lazarus",              YEAR = 2010, PEAK = 3) |>  
add_row(SONG = "Crazy In Love",                     ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
add_row(SONG = "I Don't Wanna Live Forever", ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
add_row(SONG = "Passionfruit",             ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 3) |>
add_row(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "Hips Don't Lie",                   ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 1) |>
add_row(SONG = "Into You",              ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 14) |>
add_row(SONG = "Only Girl (In The World)", ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Signs",                    ARTIST = "Drake", ALBUM = "Signs",                   YEAR = 2017, PEAK = 14) |>
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Bloodstream",        ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 2) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#15

```{r }
data.frame(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
add_row(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
add_row(SONG = "Locked Out Of Heaven",           ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Sweet Dreams",                      ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 5) |>
add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "Fake Love",                ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2015, PEAK = 10) |>
add_row(SONG = "Whenever Wherever",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 2) |>
add_row(SONG = "Drunk In Love",                     ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 9) |>
add_row(SONG = "Side To Side",          ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 4) |>
add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Passionfruit",             ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 3) |>
add_row(SONG = "Blem",                     ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 10) |>
add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
add_row(SONG = "Underneath Your Clothes",          ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 3) |>
add_row(SONG = "I Don't Wanna Live Forever", ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
add_row(SONG = "Everything Has Changed", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 7) |> 
add_row(SONG = "One Last Time",         ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 2) |>
add_row(SONG = "Crazy In Love",                     ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#16

```{r }
data.frame(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "I Don't Wanna Live Forever", ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
add_row(SONG = "Hotline Bling",            ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "I Knew You Were Trouble", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Problem",               ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
add_row(SONG = "Walk On Water",                     ARTIST = "Beyoncé", ALBUM = "Revival",             YEAR = 2017, PEAK = 7) |>
add_row(SONG = "Waka Waka (This Time For Africa)", ARTIST = "Shakira", ALBUM = "Sale el Sol",          YEAR = 2010, PEAK = 21) |>
add_row(SONG = "Sing",               ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Marry You",                      ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 11) |>
add_row(SONG = "She Wolf",                         ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 4) |>
add_row(SONG = "Side To Side",          ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 4) |>
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "Into You",              ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 14) |>
add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Billionaire",                    ARTIST = "Bruno Mars", ALBUM = "Lazarus",              YEAR = 2010, PEAK = 3) |>  
add_row(SONG = "The Lazy Song",                  ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
add_row(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#17

```{r }
data.frame(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Billionaire",                    ARTIST = "Bruno Mars", ALBUM = "Lazarus",              YEAR = 2010, PEAK = 3) |>  
add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
add_row(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "Shape Of You",       ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 1) |>
add_row(SONG = "Work It Out",                       ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 7) |>
add_row(SONG = "I Don't Wanna Live Forever", ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
add_row(SONG = "When I Was Your Man",            ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
add_row(SONG = "Underneath Your Clothes",          ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 3) |>
add_row(SONG = "Break Free", ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 16) |>
add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "God Is A Woman",        ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 4) |>
add_row(SONG = "Can't Remember To Forget",         ARTIST = "Shakira", ALBUM = "Shakira",              YEAR = 2014, PEAK = 11) |>
add_row(SONG = "The Lazy Song",                  ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#18

```{r }
data.frame(SONG = "Locked Out Of Heaven",           ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Dangerous Woman",       ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 17) |>
add_row(SONG = "Everything Has Changed", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 7) |> 
add_row(SONG = "Uptown Funk",                    ARTIST = "Bruno Mars", ALBUM = "Uptown Funk",          YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Too Good",                 ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Only Girl (In The World)", ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Thank U, Next",         ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Sweet Dreams",                      ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 5) |>
add_row(SONG = "Rude Boy",                 ARTIST = "Rihanna", ALBUM = "Rated R",                      YEAR = 2009, PEAK = 2) |>
add_row(SONG = "Bloodstream",        ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 2) |>
add_row(SONG = "Lego House",         ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2011, PEAK = 5) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "24K Magic",                      ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 5) |>
add_row(SONG = "Signs",                    ARTIST = "Drake", ALBUM = "Signs",                   YEAR = 2017, PEAK = 14) |>
add_row(SONG = "Umbrella",                 ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 1) |>
add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
add_row(SONG = "Look What You Made Me Do", ARTIST = "Taylor Swift", ALBUM = "Reputation",          YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#19

```{r }
data.frame(SONG = "Halo",                              ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 4) |>
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
add_row(SONG = "We Found Love",            ARTIST = "Rihanna", ALBUM = "Talk That Talk",               YEAR = 2011, PEAK = 1) |>
add_row(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
add_row(SONG = "I See Fire",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 13) |>
add_row(SONG = "Passionfruit",             ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 3) |>
add_row(SONG = "Blank Space", ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 4) |> 
add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Signs",                    ARTIST = "Drake", ALBUM = "Signs",                   YEAR = 2017, PEAK = 14) |>
add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
add_row(SONG = "Objection (Tango)",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 17) |>
add_row(SONG = "Break Free",            ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 16) |>
add_row(SONG = "Uptown Funk",                    ARTIST = "Bruno Mars", ALBUM = "Uptown Funk",          YEAR = 2014, PEAK = 1) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "Single Ladies (Put a Ring on It)",  ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 7) |>
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#20

```{r }
data.frame(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Whenever Wherever",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 2) |>
add_row(SONG = "Everything Has Changed", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 7) |> 
add_row(SONG = "Bloodstream",        ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 2) |>
add_row(SONG = "Hotline Bling",            ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Break Free",            ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 16) |>
add_row(SONG = "Billionaire",                    ARTIST = "Bruno Mars", ALBUM = "Lazarus",              YEAR = 2010, PEAK = 3) |>  
add_row(SONG = "No Tears Left To Cry",  ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 2) |>
add_row(SONG = "Just The Way You Are (Amazing)", ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Don't",              ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 8) |>
add_row(SONG = "Drunk In Love",                     ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 9) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
add_row(SONG = "Blem",                     ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 10) |>
add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
add_row(SONG = "Did It Again",                     ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 26) |>
add_row(SONG = "Side To Side",          ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 4) |>
add_row(SONG = "Controlla",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 18) |>
add_row(SONG = "That's What I Like",             ARTIST = "Bruno Mars", ALBUM = "24K Magic",            YEAR = 2016, PEAK = 12) |>
add_row(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#21

```{r }
data.frame(SONG = "Rude Boy",                 ARTIST = "Rihanna", ALBUM = "Rated R",                      YEAR = 2009, PEAK = 2) |>
add_row(SONG = "Crazy In Love",                     ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
add_row(SONG = "Marry You",                      ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 11) |>
add_row(SONG = "Waka Waka (This Time For Africa)", ARTIST = "Shakira", ALBUM = "Sale el Sol",          YEAR = 2010, PEAK = 21) |>
add_row(SONG = "Passionfruit",             ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 3) |>
add_row(SONG = "Uptown Funk",                    ARTIST = "Bruno Mars", ALBUM = "Uptown Funk",          YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Stay",                     ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 4) |>
add_row(SONG = "Don't Bother",                     ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 9) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "The Lazy Song",                  ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Controlla",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 18) |>
add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "Blank Space", ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 4) |> 
add_row(SONG = "God Is A Woman",        ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 4) |>
add_row(SONG = "Whenever Wherever",                ARTIST = "Shakira", ALBUM = "Laundry Service",      YEAR = 2001, PEAK = 2) |>
add_row(SONG = "Signs",                    ARTIST = "Drake", ALBUM = "Signs",                   YEAR = 2017, PEAK = 14) |>
add_row(SONG = "I See Fire",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 13) |>
add_row(SONG = "Just The Way You Are (Amazing)", ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Beautiful Liar",                   ARTIST = "Shakira", ALBUM = "B'Day",                YEAR = 2006, PEAK = 1) |>
add_row(SONG = "Can't Remember To Forget",         ARTIST = "Shakira", ALBUM = "Shakira",              YEAR = 2014, PEAK = 11) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#22

```{r }
data.frame(SONG = "What's My Name",           ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 1) |>
add_row(SONG = "The Lazy Song",                  ARTIST = "Bruno Mars", ALBUM = "Doo-Wops & Hooligans", YEAR = 2010, PEAK = 1) |>
add_row(SONG = "Look What You Made Me Do", ARTIST = "Taylor Swift", ALBUM = "Reputation",          YEAR = 2017, PEAK = 1) |> 
add_row(SONG = "Hotline Bling",            ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "She Wolf",                         ARTIST = "Shakira", ALBUM = "She Wolf",             YEAR = 2009, PEAK = 4) |>
add_row(SONG = "Walk On Water",                     ARTIST = "Beyoncé", ALBUM = "Revival",             YEAR = 2017, PEAK = 7) |>
add_row(SONG = "Don't",              ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 8) |>
add_row(SONG = "I Don't Wanna Live Forever", ARTIST = "Taylor Swift", ALBUM = "Fifty Shades Darker", YEAR = 2017, PEAK = 5) |> 
add_row(SONG = "Beautiful Liar",                   ARTIST = "Shakira", ALBUM = "B'Day",                YEAR = 2006, PEAK = 1) |>
add_row(SONG = "XO",                                ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 22) |>
add_row(SONG = "Halo",                              ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 4) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Crazy In Love",                     ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "Waka Waka (This Time For Africa)", ARTIST = "Shakira", ALBUM = "Sale el Sol",          YEAR = 2010, PEAK = 21) |>
add_row(SONG = "Passionfruit",             ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 3) |>
add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
add_row(SONG = "Everything Has Changed", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 7) |> 
add_row(SONG = "Break Free",            ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 16) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#23

```{r }
data.frame(SONG = "Crazy In Love",                     ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 1) |>
add_row(SONG = "Dangerous Woman",       ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 17) |>
add_row(SONG = "S&M",                      ARTIST = "Rihanna", ALBUM = "Loud",                         YEAR = 2010, PEAK = 3) |>
add_row(SONG = "Hips Don't Lie",                   ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 1) |>
add_row(SONG = "Love Story", ARTIST = "Taylor Swift", ALBUM = "Fearless",            YEAR = 2008, PEAK = 2) |> 
add_row(SONG = "Problem",               ARTIST = "Ariana Grande", ALBUM = "My Everything",   YEAR = 2014, PEAK = 1) |>
add_row(SONG = "Blank Space", ARTIST = "Taylor Swift", ALBUM = "1989",                YEAR = 2014, PEAK = 4) |> 
add_row(SONG = "When I Was Your Man",            ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Blem",                     ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 10) |>
add_row(SONG = "Work It Out",                       ARTIST = "Beyoncé", ALBUM = "Dangerously in Love", YEAR = 2003, PEAK = 7) |>
add_row(SONG = "7 Rings",               ARTIST = "Ariana Grande", ALBUM = "Thank U, Next",   YEAR = 2019, PEAK = 1) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Into You",              ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 14) |>
add_row(SONG = "We Found Love",            ARTIST = "Rihanna", ALBUM = "Talk That Talk",               YEAR = 2011, PEAK = 1) |>
add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
add_row(SONG = "Waka Waka (This Time For Africa)", ARTIST = "Shakira", ALBUM = "Sale el Sol",          YEAR = 2010, PEAK = 21) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "One Dance",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 1) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "Best Thing I Never Had",            ARTIST = "Beyoncé", ALBUM = "4",                   YEAR = 2011, PEAK = 3) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#24

```{r }
data.frame(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
add_row(SONG = "Don't",              ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 8) |>
add_row(SONG = "Too Good",                 ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Rude Boy",                 ARTIST = "Rihanna", ALBUM = "Rated R",                      YEAR = 2009, PEAK = 2) |>
add_row(SONG = "Walk On Water",                     ARTIST = "Beyoncé", ALBUM = "Revival",             YEAR = 2017, PEAK = 7) |>
add_row(SONG = "Halo",                              ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 4) |>
add_row(SONG = "Locked Out Of Heaven",           ARTIST = "Bruno Mars", ALBUM = "Unorthodox Jukebox",   YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Waka Waka (This Time For Africa)", ARTIST = "Shakira", ALBUM = "Sale el Sol",          YEAR = 2010, PEAK = 21) |>
add_row(SONG = "Diamonds",                 ARTIST = "Rihanna", ALBUM = "Unapologetic",                 YEAR = 2012, PEAK = 1) |>
add_row(SONG = "No Tears Left To Cry",  ARTIST = "Ariana Grande", ALBUM = "Sweetener",       YEAR = 2018, PEAK = 2) |>
add_row(SONG = "Me!", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "I Knew You Were Trouble", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "One Dance",                ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 1) |>
add_row(SONG = "Umbrella",                 ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 1) |>
add_row(SONG = "Telephone",                         ARTIST = "Beyoncé", ALBUM = "The Fame Monster",    YEAR = 2009, PEAK = 1) |>
add_row(SONG = "Jumpman",                  ARTIST = "Drake", ALBUM = "What A Time To Be Alive", YEAR = 2015, PEAK = 58) |>
add_row(SONG = "Hold On We're Going Home", ARTIST = "Drake", ALBUM = "Nothing Was the Same",    YEAR = 2013, PEAK = 4) |>
add_row(SONG = "Dangerous Woman",       ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 17) |>
add_row(SONG = "The A Team",         ARTIST = "Ed Sheeran", ALBUM = "\\+", YEAR = 2011, PEAK = 2) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


<br /><br />

# Playlist \#25

```{r }
data.frame(SONG = "Too Good",                 ARTIST = "Drake", ALBUM = "Views",                   YEAR = 2016, PEAK = 3) |>
add_row(SONG = "We Are Never Ever Getting Back Together", ARTIST = "Taylor Swift", ALBUM = "Red", YEAR = 2012, PEAK = 4) |> 
add_row(SONG = "Into You",              ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 14) |>
add_row(SONG = "Walk On Water",                     ARTIST = "Beyoncé", ALBUM = "Revival",             YEAR = 2017, PEAK = 7) |>
add_row(SONG = "Drunk In Love",                     ARTIST = "Beyoncé", ALBUM = "Beyoncé",             YEAR = 2013, PEAK = 9) |>
add_row(SONG = "Fake Love",                ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2015, PEAK = 10) |>
add_row(SONG = "Hips Don't Lie",                   ARTIST = "Shakira", ALBUM = "Oral Fixation Vol. 2", YEAR = 2005, PEAK = 1) |>
add_row(SONG = "Disturbia",                ARTIST = "Rihanna", ALBUM = "Good Girl Gone Bad: Reloaded", YEAR = 2008, PEAK = 3) |>
add_row(SONG = "You Need To Calm Down", ARTIST = "Taylor Swift", ALBUM = "Lover",               YEAR = 2019, PEAK = 2) |>
add_row(SONG = "Castle On The Hill", ARTIST = "Ed Sheeran", ALBUM = "\\÷", YEAR = 2017, PEAK = 2) |>
add_row(SONG = "Photograph",         ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 15) |>
add_row(SONG = "Best Thing I Never Had",            ARTIST = "Beyoncé", ALBUM = "4",                   YEAR = 2011, PEAK = 3) |>
add_row(SONG = "Don't",              ARTIST = "Ed Sheeran", ALBUM = "\\×", YEAR = 2014, PEAK = 8) |>
add_row(SONG = "Waka Waka (This Time For Africa)", ARTIST = "Shakira", ALBUM = "Sale el Sol",          YEAR = 2010, PEAK = 21) |>
add_row(SONG = "Blem",                     ARTIST = "Drake", ALBUM = "More Life",               YEAR = 2017, PEAK = 10) |>
add_row(SONG = "Beautiful Liar",                   ARTIST = "Shakira", ALBUM = "B'Day",                YEAR = 2006, PEAK = 1) |>
add_row(SONG = "I Knew You Were Trouble", ARTIST = "Taylor Swift", ALBUM = "Red",                 YEAR = 2012, PEAK = 2) |>
add_row(SONG = "Sweet Dreams",                      ARTIST = "Beyoncé", ALBUM = "I Am...Sasha Fierce", YEAR = 2008, PEAK = 5) |>
add_row(SONG = "FourFiveSeconds",          ARTIST = "Rihanna", ALBUM = "Anti",                         YEAR = 2016, PEAK = 3) |>
add_row(SONG = "Dangerous Woman",       ARTIST = "Ariana Grande", ALBUM = "Dangerous Woman", YEAR = 2016, PEAK = 17) |>
  kable() |>
  kable_styling(bootstrap_options = "hover", full_width = T) |>
  row_spec(1:20, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0") |>
  row_spec(0, color = "white", background = "#191414", 
           extra_css = "border-top: 1px solid #a0a0a0;border-bottom: 1px solid #a0a0a0")
```


